Title

### 2023-10-19 main.tex
last minute fixes.

To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
quantum circuits, that is,  quantum circuits in which some of the operations
depend on variable parameters~\cite{cerezo}.  These circuits play an important
part in applications such as quantum machine learning~\cite{Benedetti} and
describing general quantum transformations dependent on parameters. Substantial
research has been devoted to enhancing the efficiency of these
circuits~\cite{Rasmussen}.  \\

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the restriction that only a
controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

>>>>

*****************************************************************
*****************************************************************
*****************************************************************
To represent the algorithms implemented in quantum computers, either to
simulate a physical system or for some other purpose, one often uses a quantum
circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
quantum circuits, that is,  quantum circuits in which some of the operations
depend on variable parameters~\cite{cerezo}.  These circuits play an important
part in applications such as quantum machine learning~\cite{Benedetti} and
describing general quantum transformations dependent on parameters. Substantial
research has been devoted to enhancing the efficiency of these
circuits~\cite{Rasmussen}.  \\

@@

*****************************************************************
*****************************************************************
*****************************************************************
We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for the particular case of single-qubit Pauli channels. 
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem,
which  sets the mathematical conditions for the transformations
that can be done using a parametrized circuit with the restriction that only a
controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in
section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
